Carbon Nucleosynthesis

### 2023-05-01 thesis/main.tex
new figs

%! tex program = lualatex
\DocumentMetadata{testphase=phase-III, lang=en-US}

@@

\tagpdfsetup
{
    activate-all,
}

@@

% \usepackage[tagpdf]{axessibility}

@@

\newcommand{\et}{\gls{eta}}
\newcommand{\zet}{\gls{zeta}}
\newcommand{\sfr}{\gls{sfr}}

@@

\newglossaryentry{c11}
{
    name={C11},
    type={models},
    description={the yield set from \citet{cristallo+11,cristallo+15}. The models were run at $m= (1.3, 1.5, 2.0, 2.5, 3.0, 4.0, 5.0, 6.0)$ and $Z=(0.0001, 0.0003, 0.001, 0.002, 0.003, 0.006, 0.008, 0.01, 0.014, 0.02)$. },
}
\newglossaryentry{k10}
{
    name={K10},
    type={models},
    description={the yield set from \citet{karakas10}. Includes models run at 
    $M=(1.0, 1.25, 1.5, 1.75, 1.9, 2.25, 2.5, 3.0, 3.5, 4.0, 4.5, 5.0, 5.5, 6.0)$ and $Z=(0.0001, 0.004, 0.008, 0.02)$},
}
\newglossaryentry{v13}
{
    name={V13},
    type={models},
    description={the \agb\ yield set from \citet{ventura+13,ventura+14,ventura+18,ventura+20}. Includes models with masses $m=(1.5, 2.0, 2.5, 3.0, 3.5, 4.0, 4.5, 5.0, 6.0, 6.5, 7.0)$ and with metallicities $Z=(0.0003, 0.001, 0.002, 0.004, 0.008, 0.014, 0.04)$},
}
\newglossaryentry{k16}
{
    name={K16},
    type={models},
    description={The yield set from \citet{KL16, karakas+18}. The model is sampled at 
        $M=(0.0003, 0.001, 0.002, 0.004, 0.008, 0.014, 0.04)$
        and $Z=(0.0003, 0.001, 0.002, 0.004, 0.008, 0.014, 0.04)$
    },
}

@@

For an element X and star with mass $M$, the stellar yield $\tilde{y}$ is defined as the net production of X relative to $M$, or
\begin{equation}
    \tilde{y}_{\rm X} = \frac{M_{\rm X,\ ejected} - Z_{0, X} M_{\rm ejected}}{M}   
\end{equation}
where $M_{\rm ejected}$ and $M_{\rm X, ejected}$  are the total ejected mass of the envelope and the element X, respectively. For example, if a 1 $M_\odot$ star has $\tilde{y}_{\rm C} = 10^{-3}$, then the star will add $10^{-3}\ M_\odot$ of C to the interstellar medium. 
Although per-star yields are necessary to compute \agb{} star enrichment rates in \gce{}  models, \imf-averaged yields are useful in interpreting their predictions. For a yield $y$ from a star of mass M and initial metallicity $Z$, the \imf-averaged yield is given by 
\begin{equation} \label{eq:imf-yield}
    y_{\rm X}(Z) = 
    \int_{M_{\rm min}}^{M_{\rm max}} 
    \tilde{y}_{\rm X}(M, Z)
    \frac{dN}{dM}  \ dM
\end{equation}
where ${dN}/{dM}$ is the normalized \imf, and $M_{\rm min}$ and $M_{\rm max}$ are the minimum and maximum mass of stars, which I take to be $0.08 M_{\sun}$ and $100 M_{\sun}$ respectively. For \agb{} stars, the yields are truncated above 8 $M_{\odot}$. 
To calculate the \imf-weighted net yields, I use the Versatile Integrator for Chemical Evolution code (\VICE\footnote{\VICE~is available at \url{https://github.com/giganano/VICE}}).

>>>>

%! tex program = lualatex
\DocumentMetadata{lang=en-US}

@@

% \tagpdfsetup
% {
%     activate-all,
% }

@@

%\usepackage{axessibility}

@@

\renewcommand{\eta}{\gls{eta}}
\renewcommand{\zeta}{\gls{zeta}}

@@

\newglossaryentry{c11}
{
    name={C11},
    type={models},
    description={the yield set from \citet{cristallo+11,cristallo+15}},
}
\newglossaryentry{k10}
{
    name={K10},
    type={models},
    description={the yield set from \citet{karakas10}},
}
\newglossaryentry{v13}
{
    name={V13},
    type={models},
    description={the \agb\ yield set from \citet{ventura+13,ventura+14,ventura+18,ventura+20}},
}
\newglossaryentry{k16}
{
    name={K16},
    type={models},
    description={the yield set from \citet{KL16, karakas+18}},
}

@@

For an element X and star with mass $M$, the stellar yield $\tilde{y}$ is defined as the net production of X relative to $M$, or
\begin{equation}
    \tilde{y}_{\rm X} = \frac{M_{\rm X,\ ejected} - Z_{0, X} M_{\rm ejected}}{M}   
\end{equation}
where $M_{\rm ejected}$ and $M_{\rm X, ejected}$  are the total ejected mass of the envelope and the element X, respectively. For example, if a 1 $M_\odot$ star has $\tilde{y}_{\rm C} = 10^{-3}$, then the star will add $10^{-3}\ M_\odot$ of C to the interstellar medium. 
Although per-star yields are necessary to compute \agb{} star enrichment rates in \gce{}  models, \imf-averaged\footnote{IMF: Initial Mass Function} yields are useful in interpreting their predictions. For a yield $y$ from a star of mass M and initial metallicity $Z$, the \imf-averaged yield is given by 
\begin{equation} \label{eq:imf-yield}
    y_{\rm X}(Z) = 
    \int_{M_{\rm min}}^{M_{\rm max}} 
    \tilde{y}_{\rm X}(M, Z)
    \frac{dN}{dM}  \ dM
\end{equation}
where ${dN}/{dM}$ is the normalized \imf, and $M_{\rm min}$ and $M_{\rm max}$ are the minimum and maximum mass of stars, which I take to be $0.08 M_{\sun}$ and $100 M_{\sun}$ respectively. For \agb{} stars, the yields are truncated above 8 $M_{\odot}$. 
To calculate the \imf-weighted net yields, I use the Versatile Integrator for Chemical Evolution code (\VICE\footnote{\VICE~is available at \url{https://github.com/giganano/VICE}}).
